---
title: "Basil Forecast: Synthetic Demonstration"
author: "Maxfield Raynolds"
format: html
editor: visual
---

```{r}
#| include: false
library('fpp3')
library('tidyverse')

source('R/forecast_pipeline.R')
```

In order to demonstrate the functions of the app and forecast, functions from the forecast_pipeline are used in this quarto document. The synthetic data is loaded into the environment below.

```{r}
#| message: false
issue_date <- as.Date('2026-09-29')
model_start <- as.Date('2021-07-26')

demo_raw <- read_csv('basil_synthetic_demo.csv',
                     col_types = readr::cols(
                       HarvestDate = readr::col_date(format = '%Y-%m-%d'),
                       LineNumber = readr::col_double(),
                       ProductID = readr::col_double(),
                       AvgHeadweight = readr::col_double()
                     )
)
```

Invalid weights are flagged.

```{r}
invalid_weights <- find_invalid_weights(demo_raw)
```

Flagged weights are replaced with missing values; the original records and weights are retained.

```{r}
demo_clean <- clean_basil_weights(demo_raw, invalid_weights)
```

The cutoff date for the data to be used in forecasting is applied, and the observations are aggregated.

```{r}
demo_weekly <- prepare_basil_weekly(demo_clean, issue_date)
```

The forecast applies the modeling start date.

```{r}
demo_forecast <- forecast_basil(
  demo_weekly,
  issue_date,
  model_start
)
```

Then it is prepped for display.

```{r}
demo_display <- make_forecast_display(demo_forecast)
```

The table below enumerates the forecast and the lower and upper bounds of an 80% and 95% prediction interval.

```{r}
#| echo: false
demo_display |> 
  transmute(
    `Harvest week starting` = as.character(as.Date(week)),
    `Forecast (g)` = .mean,
    `80% lower` = lower80,
    `80% upper` = upper80,
    `95% lower` = lower95,
    `95% upper` = upper95
  ) |> 
  knitr::kable(digits = 1)
```

The same table information is plotted below.

```{r}
#| echo: false
demo_display |> 
  mutate(
    week_start = as.Date(week)
  ) |> 
  ggplot(aes(x = week_start)) + 
  geom_ribbon(aes(ymin = lower95, ymax = upper95), fill = 'orange', alpha = 0.15) + 
  geom_ribbon(aes(ymin = lower80, ymax = upper80), fill = 'orange', alpha = 0.30) +
  geom_line(aes(y = .mean)) +
  labs(
    x = 'Harvest week starting',
    y = 'Reported head-weight index (g)',
    title = 'Basil Forecast Synthetic Data',
    subtitle = 'Darker band: 80% prediction interval; lighter band: 95%'
  )
```

The flat prediction is expected. The naive model uses the latest observed weekly index for every future week. The widening bands represent model-based prediction intervals. These synthetic results demonstrate the workflow, not operational forecast accuracy. The index is an approximation based on reported sample averages and does not estimate total production.
